Covariate analysis of ROSMAP RNASeq

### 2016-01-25 code/Rmd/ROSMAP_RNASeq.Rmd
Minor modifications

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Batch), shape=as.factor(cogdx), size=as.numeric(age_death)))
p <- p + theme_bw() + theme(legend.position="top") 
p <- p + geom_text(aes(label= Sampleid), size=4, hjust=1)
p

@@

```{r residualSigCovars.manual.ALL, fig.width=15, fig.height=8}
residualSigCovars[["PC_res"]][[2]]$plotData
```

```{r addVarsBack}
varsToAddBackIn <- c("cogdx1",  "cogdx2", "cogdx3", "cogdx4", "cogdx5", "cogdx6")
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + t(data.matrix(DESIGN[,varsToAddBackIn]) %*% t(FIT$coefficients[,varsToAddBackIn]))
RESIDUAL.GENE_EXPRESSION = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'EnsemblGeneID') %>%
  tidyr::separate(col = EnsemblGeneID, into = c('ensembl_gene_id','position'), sep = '\\.')
```

>>>>

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Batch), shape=as.factor(cogdx), size=as.numeric(age_death)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= Sampleid), size=4, hjust=1)
p

@@

```{r residualSigCovars.manual.ALL, fig.width=15, fig.height=8}
residualSigCovars[["PC_res"]][[2]]$plotData
```
Adding cogdx back to the residuals
```{r addVarsBack}
varsToAddBackIn <- c("cogdx1",  "cogdx2", "cogdx3", "cogdx4", "cogdx5", "cogdx6")
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + t(data.matrix(DESIGN[,varsToAddBackIn]) %*% t(FIT$coefficients[,varsToAddBackIn]))
RESIDUAL.GENE_EXPRESSION = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'EnsemblGeneID') %>%
  tidyr::separate(col = EnsemblGeneID, into = c('ensembl_gene_id','position'), sep = '\\.')
```

### Clustering residual gene expression
```{r decompse.normalise.data1, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1:2)], scale.=T)

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Batch), shape=as.factor(cogdx), size=as.numeric(age_death)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= Sampleid), size=4, hjust=1)
p

tree = hclust(as.dist(t(RESIDUAL.GENE_EXPRESSION[,-(1:2)])))
plotDendroAndColors(tree, 
                    colors = labels2colors(COVARIATES.tmp), 
                    dendroLabels = FALSE, 
                    abHeight = 0.80, 
                    main = "Sample dendrogram",
                    groupLabels = colnames(COVARIATES.tmp))
```
